Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-07-26 analysis/paper/paper.Rnw
added R code to read expr file

<<read_attie_files>>=
lod_peaks <- readRDS(here("analysis", "data", "derived_data", "lod_peaks.rds"))
annots <- readRDS(here("analysis", "data", "derived_data", "annots.rds"))
@

>>>>

<<read_attie_files>>=
lod_peaks <- readRDS(here("analysis", "data", "derived_data", "lod_peaks.rds"))
annots <- readRDS(here("analysis", "data", "derived_data", "annots.rds"))
expr <- readRDS(here("analysis", "data", "derived_data", "expr.rds"))
@
